\documentclass[12pt,]{scrartcl}
\usepackage{longtable}
\usepackage{lmodern}
\usepackage{multicol}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}

% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\PassOptionsToPackage{hyphens}{url} % url is loaded by hyperref
\usepackage[unicode=true]{hyperref}
\hypersetup{
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage[margin=1in]{geometry}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\usepackage{fontspec}
\defaultfontfeatures{Scale=MatchLowercase,Ligatures={TeX}}
\setmainfont{Liberation Serif}
\setsansfont{Liberation Serif}
\setmonofont[SmallCapsFont={Liberation Serif}]{Liberation Serif}
\usepackage{hyperref}
\usepackage{multirow}
\usepackage{xcolor}
\definecolor{cvlinkcolor}{RGB}{6,125,233}
\hypersetup{colorlinks,linkcolor=cvlinkcolor,citecolor=cvlinkcolor,urlcolor=cvlinkcolor,bookmarksnumbered,bookmarks=false,pdfinfo={Title={Curriculum Vitae},Author={Lighton Phiri},Creator={Lighton Phiri},Subject={Curriculum Vitae},Keywords={Curriculum Vitae},CreationDate={D:20150513232724}}}
\renewcommand\labelenumi{[\theenumi]}

\date{}
\begin{document}


\begin{table}[h]
%%%\centering
{\def\arraystretch{1.2}\tabcolsep=0pt
\begin{tabular}{p{0.50\linewidth}p{0.20\linewidth}p{0.25\linewidth}}

  \multirow{1}{*}{\LARGE \textbf{Mansura Habiba}} &  &  \\
  
  & & \\
  
Principal Platform Architect (AI, HPC, Cloud) & \multicolumn{1}{r}{Linkedin:\;\;}  & \multicolumn{1}{l}{\href{https://www.linkedin.com/in/mansura-h-a0174a19}{@MansuraHabiba}} \\
  
  IBM in Ireland, Dublin, Ireland & \multicolumn{1}{r}{Email:\;\;} &\multicolumn{1}{l}{\href{}{}} \\


  Patents, Publications are listed in \href{https://scholar.google.com/citations?user=oee3rpwAAAAJ}{Google Scholar} & \multicolumn{1}{r}{twitter:\;\;}  & \multicolumn{1}{l}{\href{https://twitter.com/MansuraHabiba}{@MansuraHabiba}} \\

Published book: \href{https://packt.link/a/9781803248318}{Hybrid Cloud Infrastructure and Operations Explained} & \multicolumn{1}{r}{ Badges:\;\;}  & \multicolumn{1}{l}{\href{https://www.credly.com/users/mansura-habiba/badges}{Professional Badges in Credly}}\\

 & \multicolumn{1}{r}{ Mobile No:\;\;}  & \multicolumn{1}{l}{+353899822405}\\
\end{tabular}%
}
\end{table}

\vspace{0.3cm}

\section*{Who is Mansura?}

Mansura has 15+ years of experience in the technology industry. She has played the role of cloud-native solutions architect, technical lead, lead engineer and software engineer. She has experience in solution design, application development, innovation, research and development. She is experienced in different industries, such as software design and development, telecommunication, healthcare, finance and banking, workforce, and energy. She is highly skilled in Artificial Intelligence, hybrid cloud, OpenShift, cloud-native development and solution design, Platform Architecture design and platform engineering.  She is an Open Group Certified Architect and has several public cloud certifications. She is also a certified IBM Cloud and Cloud PAK Systems architect.

While at IBM (2014-Present), she played different roles as a software engineer, technical lead, solution architect, and platform architect for AI and HPC platforms. She is active in the IBM mentoring program and regularly helps others by mentoring them on technology skills and providing career guidance. She has participated in several IBM Academy of Technology (AoT) initiatives and exhibits thought leadership. She has presented several talks for both internal and external audiences. She has won different awards at IBM and in her previous roles. She regularly participated in patent submission and idea sessions with fellow IBMers. She is also involved in various innovation initiatives at IBM, including emerging technologies such as deep learning, artificial intelligence, big data, image processing, and blockchain.

She is currently playing the role of a Lead Platform architect for complex Cloud solution-focused opportunities involving multiple disciplines or business units in IBM. She provides leadership and direction to high-priority or special projects the business undertakes. She leads the operation and management engineering process optimisation by implementing GenAI for different operations activities, i.e. providing continuous observability, troubleshooting, self-healing and optimization of the HPC platform. Currently, she is also responsible for defining the SLAs, practices, processes, tools, and technical foundation of IBM's managed services for platform operations. She leds the platform engineering and operations for some of the world's largest organizations, including the top 5 global banks, a leading car manufacturing company in Germany, and a significant energy and power grid supplier in the US. These platforms were deployed across IBM Cloud, AWS, and Azure, where she ensured the seamless integration of operations, compliance with SLAs, and continuous optimization of performance, security, and scalability. Her role also involved overseeing the end-to-end architecture and managing cross-functional teams to meet the complex requirements of these industries. She is leading the delivery engineering team for various operations and engineering activities (i.e. modernization, containerization, Automation validation, Patching, Security and Privacy management and others), including a team of 45 members across the globe in India, China, Mexico and Egypt In addition, she is also responsible for presenting the customer with suitable recommendations for IT management and appropriate technological alternatives and evaluating new technological developments and evolving business requirements.

She has completed her PhD in deep learning and has published several research papers on secured cloud-based architecture, natural disaster management systems, and other applications. 

Mansura Habiba is a published author focusing strongly on AI and cloud technologies. Her most recent book, "Hybrid Cloud Infrastructure and Operations Explained: Accelerate Your Application Migration and Modernization Journey on the Cloud with IBM and Red Hat" (2022), provides comprehensive insights into cloud architecture, cloud migration strategies, and how businesses can leverage IBM and Red Hat technologies for modernization. It is an essential guide for organizations looking to enhance their cloud capabilities and streamline their infrastructure.

Currently, Mansura is working on a new book that delves into the intersection of AI operations and cloud platforms. This upcoming work will explore how organizations can implement and scale AI-driven solutions within cloud environments, tackling key challenges such as automation, cybersecurity, and real-time analytics. With her deep expertise in AI, high-performance computing, and cloud strategy, the book aims to offer practical insights and strategies for organizations to realize the full potential of AI in cloud-based architectures.

She is also a reviewer and editorial board member for several IEEE journals and conference publications, including multiple international journals. So far, she has filed twelve patents on Neural Networks, Workload Migration, Security, Blockchain, Quantum computing, Edge computing, and Sustainability. She also has some patents currently under review on Generative AI. 

For her next role, Mansura Habiba aims to take on a leadership position as a Technical Lead, where she can guide AI adoption across various products to address real-world challenges. Her focus will be on creating practical, agile AI solutions that are both scalable and ethically sound. Drawing on her extensive experience in AI architecture and cloud-based operations, Mansura seeks to drive innovation while ensuring that AI is applied responsibly and with clear business impact. This role would allow her to combine her technical expertise with her passion for solving complex problems through cutting-edge technology.

\vspace{0.3cm}

\section*{Key Skills}
\begin{itemize}

    \item \textbf{Managed Operations:} Leading large-scale enterprise platform operations on cloud (AWS, Azure, IBM Cloud and GCP), optimizing costs, improving security, and ensuring performance and leading incident management including critsit and Major Incident Management (MIM). Leading the design and implementation of central observability solutions using Grafana, Instana, DataDog, and cloud-native monitoring. Hands-on experience in implementing automation for 24/7 operations using Ansible and Terraform.
    \item \textbf{High-Performance Computing (HPC):} Design and optimization of HPC platforms, implementing AI-driven automation and observability for workload management. Hands-on experience in Symphony, Scale, LSF and other HPC software.
    \item \textbf{Generative AI \& AI Strategy:} Implemented AI workflows for automated cloud operations, contributing to \$500K annual cost savings.
    \item \textbf{Artificial Intelligence Core Competencies:} Expertise in CNNs, RNNs, GANs, Neural ODEs, LSTMs, and Transformer models. Also experienced with NLP tools such as SpaCy, NLTK, Hugging Face, and IBM Watson. She has strong experience in Tensorflow, Pytorch, jupyter, Jax, numpy and other libraries. She has Hands-on experience in in anomaly detection, threat detection, and automated incident response using AI.
    \item \textbf{AI Tools \& Platforms}: Hands-on experience in TensorFlow, PyTorch, Keras, Scikit-learn,  IBM Watson, AWS SageMaker, Google AI Platform, and Microsoft Azure AI. She is skilled in model deployment with Docker and Kubernetes and automation of ML pipelines using Kubeflow and MLflow. She has Hands-on experience in data preprocessing, feature engineering, and handling large datasets using Pandas, NumPy, and Spark.
    \item \textbf{AI Strategy \& Leadership}: Experience in leading AI adoption strategies aligned with business goals and operational efficiency. She led the development and adoption of AI for the platform engineering operations using AIOps. 

    \item \textbf{Site Reliability Engineering :} Led SRE team of 45 engineers for the world's largest Banking, automobile, and energy supplier clients. Define SRE practice and standards, perform maturity analysis for the organization and team and define the roadmap for improvement.   
    
    \item \textbf{Software Development:} Proficient in Java, Python, C++, R, and Go for distributed computing, RESTful API, Neural network Modelling, MLOPs, DevOps, Container platform, e.g. Docker, Kubernetes and OpenShift; and cloud-native applications development.
    
    \item \textbf{Leadership:} Proven ability to lead cross-functional global teams (45+ members), driving projects across finance, government, telecom, and healthcare industries.
\end{itemize}


\vspace{0.3cm}

\section*{Education}
\noindent \textbf{Ph.D. in Deep Learning, University of Maynooth, Ireland} \\
Thesis: Neural Ordinary Differential Equations for Continuous Time Series

\noindent \textbf{M.Sc. in Software Engineering, American International University, Bangladesh}\\
Thesis: Exploring Cloud-Based Disaster Management

\noindent \textbf{B.Sc. in Computer Science and Engineering, University of Khulna, Bangladesh}

\vspace{0.3cm}

\section*{Professional Experience}

\subsection*{Principal Platform Architect, AI and HPC platform, Hybrid Cloud Management Managed Service, IBM | 07/2022 -- Present}
\begin{itemize}
   \item Led the design, development, and implementation of platform engineering solutions using various cutting-edge technologies, including cloud platforms, AI, and container orchestration systems, to meet the needs of large-scale enterprises.
   \item Led the design and architecture of managed services platforms across IBM Cloud, AWS, and Azure for high-profile clients, including top 5 global banks, a leading German car manufacturer, and a major US energy and power grid supplier.
    \item Led design and implementation of central observability solution, automation for 24X7 operations for the platform to keep the up-time maximum.
    \item Led the operation and management engineering process optimisation by implementing GenAI for different operations activity, i.e. providing continuous observability, troubleshooting, self-healing and optimization of the HPC platform. 
    \item Led delivery engineering team for different operations and engineering activities (i.e. modernization, containerization, Automation validation, Patching, Security and Privacy management and others), including a team of 45 members across the globe in India, China, Mexico and Egypt. 
    \item Spearheaded designing and implementing AI-driven HPC solutions for IBM clients, optimizing performance and reducing operational costs.
    
    \item Established and defined key performance indicators (KPIs) and service-level agreements (SLAs) to scale businesses, ensuring transparency and reporting to senior leadership.
\item Ensured compliance with these metrics, driving operational excellence and consistent service delivery.
\item Led the implementation of centralized proactive monitoring and continuous improvement processes to maintain high operational standards and minimize downtime.
\item Developed end-to-end system designs that focused on performance, security, and scalability to meet industry-specific requirements.

\item Designed and Implemented features for operation management using AWS, IBM Cloud, Azure cloud services, OpenShift and Kubernetes container platform in addition to Ansible on the RedHat Ansible Automation Platform.

    \item Led multiple workstreams across functional and geographic divisions, aligning platform engineering efforts with larger business strategies and ensuring consistent execution and delivery.
\item Drove cross-functional collaboration between AI, cloud, and software engineering teams, ensuring seamless integration of solutions across divisions.
\end{itemize}

\subsection*{Platform Architect, Offering Lead, Hybrid Cloud Management Managed Service, IBM | 10/2021 -- 06/2022}
\begin{itemize}
    \item Designed hybrid cloud solutions integrating AWS, Azure and IBM Cloud services, providing migration strategies for public and private sectors.
    \item Collaborated with reference architects and led technical engagements, advising on cloud-native reference architectures and best practices.
    \item Developed roadmaps for cloud cost optimization and disaster recovery strategies using AWS, Azure and IBM Cloud Services.
    \item Managed large-scale OpenShift and Kubernetes deployments, ensuring seamless cloud migration and system modernization.
    \item As the Offering Lead for IBM Platform Engineering Services and Center of Competency, Spearheaded the design, development, and implementation of platform engineering solutions using a variety of cutting-edge technologies, including cloud platforms, AI, and container orchestration systems, to meet the needs of large-scale enterprises.
    \item Provided strategic thinking and leadership in building scalable and resilient solutions for enterprise clients, ensuring alignment with both business and technological goals.
    \item Led the creation of roadmaps for AI and platform modernization solutions, ensuring these aligned with IBM's broader business objectives.
    \item Delivered executive-level updates to senior management on high-visibility projects and initiatives, ensuring timely communication and strategic alignment with company objectives.
    \item Recruited and built a high-performing team of engineers, ensuring that new hires had the right mix of skills and expertise to drive innovation and meet client needs.
    \item Fostered a culture of open feedback, coaching, and mentorship for engineers at all levels, ensuring they had the support needed to grow professionally and stay at the forefront of industry trends.
    \item Managed and optimized budgets, ensuring accurate forecasting and cost allocation while delivering on business needs. This involved balancing resource allocation across multiple projects and ensuring alignment with company goals.
    \item Set a vision for a culture of innovation within the platform engineering services, encouraging my team to challenge conventional approaches and explore new methodologies, such as AI-driven automation, distributed ledger technology, and microservices architecture.
    \item Engaged in thought leadership initiatives within IBM and externally, contributing to industry discussions on platform architecture, AI, and cloud technologies. Led comparative analysis and benchmarking for the business against competitors.
\end{itemize}

\subsection*{Lead Solution Architect, IBM | 01/2020 -- 10/2021}
\begin{itemize}
    \item Led Hybrid cloud migration projects for multiple industries, helping clients transition to cloud infrastructure by integrating Cloud services.
    \item Solution significant deals for cloud modernization across the healthcare, finance, and telecom sectors, driving \$500M+ in revenue.
    \item Defined reference architectures for scalability, security, and cost efficiency during cloud migration projects.
    \item Established technical reference architectures for Cloud Native and OpenShift-based application modernization on AWS, Azure and IBM Cloud Services.
    \item Led the architecture and design of cloud platform solutions, migration and modernization solutions, containerization solutions, and deep learning solutions - driving innovation in artificial intelligence applications.
    
   \item Led designing and deploying highly available and resilient OpenShift clusters tailored to the specific needs of enterprise clients in finance (insurance, banking), retail, energy and government industry-based clients. These solutions included on-premises and cloud-based deployments, ensuring compatibility with hybrid or multi-cloud strategies.
   \item Implemented best practices for security, including multi-cluster management (up to 50 clusters) across global platforms, network policies, and compliance with industry standards, ensuring that OpenShift clusters were secure and aligned with organisational policies.
   \item Defined and standardised practices, processes and tools for platform operations using concepts like MLOps, SRE and Platform engineering
\end{itemize}

\subsection*{Technical Lead, Software Engineer, IBM | 11/2017 -- 12/2019}
\begin{itemize}
      \item Led the modernization of the IBM Watson career application by leveraging Kubernetes and cloud-native services. 
     \item Led a team of Senior Software Engineers, DevOps, and QA in IBM Software Group, driving the adoption of cognitive applications for IBM's largest banking, insurance, and investment banking clients.
     \item Led a multi-disciplinary team for Application Modernization and Enterprise adoption, designing solution architecture for Application Deployment, Security, Network, DevOps Pipeline, Scalability, Backup, and Disaster Recovery.
     \item Implemented Algorithms based on deep learning and other AI concepts such as NLP, pattern recognition, and identification of bias to improve AI transparency. 
     \item Implemented a database backup and disaster recovery solution, developed a micro-service for Bulk Data Ingestion to the Data Lake, and deployed applications using the DevOps pipeline on the Kubernetes cluster.
     \item Led the strategic product management and defining business strategy for customers. Led and coached technical teams for client success with IBM software.
     \item Developed proofs-of-concept for customer presentations and internal research, designed schema and map-reduce functions for the NoSQL database, and actively participated in collaboration workshops with customers to explore technical solutions.
     \item Led client communication for use case identification and new feature requirements for cognitive AI applications. Assessed the feasibility of those new feature requirements for the product to be included in the road map. Revised the road map for the product with the offering manager and finalised them.
    \item Mentored several IBMers for Angular, Nodejs, R, Cloudant, Blockchain, Design Thinking, IBM cloud and Kubernetes and career progression. Mentored transition year students for a challenge day project. 
    
\end{itemize}

\subsection*{Staff Software Engineer, IBM | 09/2014 -- 10/2017}
\begin{itemize}
\item Developed web and J2EE applications using technologies such as J2EE, IBM Cloudant, IBM Cloud Object Storage, IBM Kubernetes Service, Angular, Nodejs, CSS, Swagger, microservices, IBM Design Thinking, and Agile.
 \item Developed and enhanced data insight platforms, incorporating advanced analytics, visualization, and reporting functionalities to provide actionable insights for stakeholders.
 \item Led design thinking and agile methods in the day-to-day engineering processes for the project. 
\item Mentored several IBMers for Angular, Nodejs, R, Cloudant, Blockchain, Design Thinking, IBM cloud and Kubernetes and career progression. Mentored transition year students for a challenge day project. 
    
\end{itemize}



\subsection*{Senior Software Engineer Consultant, Cimsolutions B.V. | 05/2013 -- 09/2014}
\begin{itemize}

\item Developed applications and delivered multiple projects for the Dutch Finance Ministry, Group2000 B.V and Astron.
 
\item For the Duch Finance Ministry, I developed functionalities for a web portal to integrate the Dutch government with the Pan European Proxy Service (PEPS) for mijnrvo and klap portal as part of the e-recognition tool for entrepreneurs in EURO countries (eHerkenning) upgrade project. I developed functionalities using Java, Maven, Ant, SAML, Oracle Single Sign-On (OSSO), Spring, Struts 2, JSF and Java Security.

\item Developed components for software-defined network functionalities for telecommunication providers in the Netherlands through Group 2000 BV using Java, Groovy, Grails, Test Driven Development and Agile. 

 \item  For Astron, I developed a web-based proposal submission system (NorthStar). This web portal was mainly for astronomers to submit the proposal to access the data from the Lofar satellite using J2EE, Spring, Tomcat, Hibernate, JSF, Jquery, HTML, CSS, Maven, Ant, RedMine, Jenkins, TDD and Agile. Astron invited me for the second time. During my second contract with Astron, I implemented algorithms to schedule the observation time of the Lofar satellite based on the requested data and time submitted by astronomers to access the Lofar satellite optimally.

\end{itemize}


\subsection*{Lead Engineer, Tech Lead, Samsung R\&D Institute, Bangladesh |11/2012--03/2013 }

\begin{itemize}
 \item Led multi-disciplinary teams of engineers specializing in Wifi/GPS, SyncMl, and Bluetooth/NFC technologies as a Technical Lead.
 \item Drove the development and improvement efforts for communication protocols, including Bluetooth, WiFi, WiFi Direct, NFC, GPS, SyncML, Device Encryption, Device Synchronization, and Fotaclient, for multiple major Samsung smartphone releases.
 \item Led the R\&D network team for the feature implementation, troubleshooting and configuration management for 14 smartphone models, including S4, S3, S2-NFC, Note II, etc.
 \item Developed mobile applications addressing various NFC Tag, SyncML, Bluetooth, and WiFi use cases, utilizing Java, Android, and C++.
 
\end{itemize}

\vspace{0.3cm}

\subsection*{Senior Software Engineer, Grameen Solutions Limited, Bangladesh |01/2011--09/2011}
\begin{itemize}
    \item Developed Mobile Financial Solutions using the Macalla platform (Roamware). Worked on developing mobile financial solutions for several banks (e.g ecobank) and telecommunication operators (STC Telecom Kuwait, Al-Bahar Telecom Kuwait, Vodaphone Romania) using J2EE, JSP, JSF, Spring, XML, Struts 2, XHTML, Hibernate, JasperReport, JUnit, JQuery, Castor, JDOM, J2ME, AJAX, Ant, Oracle, PL/SQL, MVC, design patterns, SoapUi, Toad, Eclipse, Apache Tomcat, iReport, Adobe Illustrator, CVS, SVN, SSh Secure Shell Client, Target Process and Agile.
   \item 	Designed and implemented workflow for BPM processes, Use case and Database schema Web Services, adapter, and gateway implementation for different new features. I also participated in peer programming and code review for team members. 
   \item 	Provided post-release support for other clients of m-commerce in all instances, including training where necessary; Provided emergency troubleshooting for customer
   \item 	 Collaborated with distributed team members over Ireland, India and Bangladesh to define product coding standards, system and internationalization requirements;


\end{itemize}


\section*{Books}
\begin{itemize}
    \item \textbf{Book:} \emph{Hybrid Cloud Infrastructure and Operations Explained}, Packt Publishing, 2022.
    \item Published multiple research papers and patents on AI and cloud migration strategies.
\end{itemize}

\subsubsection{Book chapters}\label{book-chapters}

\begin{enumerate}
  %%%%%\leftskip-0.25in % for bullets
  \leftskip-0.13in % for numbers
  \item \textbf{Habiba, M}., \& Akter, S. (2018). Exploring Cloud-Based Distributed Disaster Management With Dynamic Multi-Agents Workflow System,Smart Technologies for Emergency Response and Disaster Management. (pp. 167-195). IGI Global.
\end{enumerate}


\vspace{0.3cm}

\subsection{Patents}

\begin{itemize}
    \item WO2023105384A1 - Blockchain clock for storing event data - IBM
    \item WO2023072443A1 - Workload migration - Kyndryl, Inc.
    \item US20230088588A1 - Security as a service for machine learning - IBM
    \item US20240161000A1 - Artificial intelligence-based sustainability control - IBM
    \item US11902331B2 - Request authorization - IBM
    \item US20230205829A1- Recommending and performing personalized component arrangements -Kyndryl, Inc.
    \item Filed - A method for applying and enforcing location-aware, automatic data governance/regulatory controls on edge nodes - IBM
    \item Filed - No-Code solution deployment based on Natural Language Processing, Recommendation Knowledge and Infrastructure as a Code - IBM 
    \item Filed - A Method and System for Real-Time Adjustment of Regulatory Policies, controls and Deployment Pattern - IBM 
    \item Filed - Dual quantum recurrent neural network system with attention for time series prediction - IBM
\end{itemize}


\subsection{Publications}\label{publications}

%%\emph{Preprint URLs available at
%%\url{http://orcid.org/0000-0003-3582-9866}}\\
\subsubsection{Journals}\label{journals}

\begin{enumerate}
  %%%%%\leftskip-0.25in % for bullets
  \leftskip-0.13in % for numbers
  \item \textbf{Habiba, M}.; Islam, Md R.; Ali, ABM S.; (2018). A component based unified architecture for utility service in cloud , Future Generation Computer Systems, vol. 87, (pp. 725--742). DOI: \href{https://doi.org/10.1016/j.future.2017.10.017}{10.1016/j.future.2017.10.017}
  %%%
  \item \textbf{Habiba, M}.;  Islam, Md R.;  Ali, ABM S.; Islam, Md Z.; (2016). A New Approach to Access Control in Cloud,  Arabian Journal for Science and Engineering, vol. 41, issue. 3, (pp. 1015--1030), Springer, Berlin, Heidelberg. DOI: \href{https://doi.org/10.1007/s13369-015-1947-8}{10.1007/s13369-015-1947-8}
  
   \item Islam, Md R.;  \textbf{Habiba, M}. (2014). Data Intensive Dynamic Scheduling Model and Algorithm for Cloud Computing Security , Journal of Computers Program (JCP), vol. 9 issue. 8, (pp. 1796--1808). DOI: \href{https://doi.org/10.4304/jcp.9.8.1796-1808 }{10.4304/jcp.9.8.1796-1808 }
\end{enumerate}

\subsubsection{Conferences}\label{conferences}

\begin{enumerate}
  %%%%%\leftskip-0.25in % for bullets
  \leftskip-0.13in % for numbers
  
   \item \textbf{Habiba, M}; Pearlmutter, BM; (2020). Neural ODEs for Informative Missingness in Multivariate Time Series, Irish Signal and System Conference, 2020 ; ISSC2020; 
  
  \item \textbf{Habiba, M}; Pearlmutter, BM; (2020). Neural Ordinary Differential Equation based Recurrent Neural Network Model, Irish Signal and System Conference, 2020 ; ISSC2020;
  \item Islam, Md R.; \textbf{Habiba, M}. \& Kashem, Mir I. I.; (2017). A framework for providing security to Personal Healthcare Records, international conference on networking, systems and security (NSysS) (pp. 168--173). DOI: \href{https://doi.org/10.1109/nsyss.2017.7885820 }{10.1109/nsyss.2017.7885820}
  
  
   \item \textbf{Habiba, M}.; \& Islam, Md R.; Ali, ABM S.; (2015). Access control management as a service for NoSQL big data, Asia-Pacific World Congress on Computer Science and Engineering (APWC on CSE), (pp. 1--7). DOI: \href{https://doi.org/10.1109/apwccse.2015.7476244 }{10.1109/apwccse.2015.7476244}
  
   \item \textbf{Habiba, M}.; \& Islam, Md R.; Ali, ABM S.; (2014). A unified architecture for utility service in cloud, Asia-Pacific World Congress on Computer Science and Engineering (APWC on CSE), (pp. 1--8). DOI: \href{https://doi.org/10.1109/apwccse.2014.7053848 }{10.1109/apwccse.2014.7053848}
 
  \item Opu, Md F.R.; Biswas, E. ; \textbf{Habiba, M}.;Kim, C.; (2013). Architecture of a context aware framework for automated mobile device configuration, International Conference on Grid and Pervasive Computing, (pp. 299--308). DOI: {https://doi.org/10.1007/978-3-642-38027-3\_32  }{10.1007/978-3-642-38027-3\_32}
 
 \item \textbf{Habiba, M}.; \& Islam, Md R.; Ali, ABM S.; (2013). Access control management for cloud, 12 $^{th}$ IEEE International Conference on Trust, Security and Privacy in Computing and Communications, (pp. 485--492). DOI: \href{https://doi.org/10.1109/trustcom.2013.61 }{10.1109/trustcom.2013.61 }

  \item \textbf{Habiba, M}.; \& Akhter, S.; (2013). A cloud based natural disaster management system, International Conference on Grid and Pervasive Computing, (pp. 152--161), Springer, Berlin, Heidelberg. DOI: \href{https://doi.org/10.1007/978-3-642-38027-3\_16  }{10.1007/978-3-642-38027-3\_16}
   
   \item Islam, Md R.; \textbf{Habiba, M}.; (2012). Dynamic scheduling approach for data-intensive cloud environment, International Conference on Cloud Computing Technologies. Applications and Management (ICCCTAM), (pp. 179--185). DOI: \href{ https://doi.org/10.1109/iccctam.2012.6488094  }{10.1109/iccctam.2012.6488094}
  
  
  \item \textbf{Habiba, M}.; \& Akhter, S.; (2012). MAS workflow model and scheduling algorithm for disaster management system, International Conference on Cloud Computing Technologies. Applications and Management (ICCCTAM), (pp. 164--173). DOI: \href{https://doi.org/10.1109/iccctam.2012.6488092 }{10.1109/iccctam.2012.6488092}

    \item Islam, Md R.; \textbf{Habiba, M}.; (2012). Collaborative swarm intelligence based Trusted Computing, International Conference on Informatics, Electronics \& Vision (ICIEV) (pp. 1--6). DOI: \href{https://doi.org/10.1109/iciev.2012.6317341  }{10.1109/iciev.2012.6317341 }

 \item \textbf{Habiba, M}.; (2012). Metrics for evaluating agent oriented software engineering model, International Conference on Informatics, Electronics \& Vision (ICIEV), (pp. 17--22). DOI: \href{ https://doi.org/10.1109/iciev.2012.6317459 }{10.1109/iciev.2012.6317459 }
 
  \item Islam, Md R. \textbf{Habiba, M}.,(2012). Agent based framework for providing security to data storage in cloud, 15$^{th}$ International Conference on Computer and Information Technology (ICCIT) (pp. 49--58). DOI: \href{https://doi.org/10.1109/iccitechn.2012.6509712 }{10.1109/iccitechn.2012.6509712 }

\end{enumerate}



 \subsubsection{ Public Talk / Presentation}\label{theses-and-dissertations}

 \begin{enumerate}
  %%%%%\leftskip-0.25in % for bullets
  \leftskip-0.13in % for numbers
   \item \textbf{Habiba, M.}. (2019). Deep learning with PyTorch. PyLadies Meetup Group. Dublin, Ireland. Presentation Available on \href{https://github.com/mansura-habiba/meetup/tree/master/PyLadies_Dublin_2019}{Github}.
   \item \textbf{Habiba, M}. \& Li, Y. (2015). Social Analytic using NodeJs + R. Nodejs Meetup Group. Dublin, Ireland. Presentation Available on \href{https://github.com/mansura-habiba/meetup/blob/master/Nodejs_meetup_dublin.pptx}{Github}.
\end{enumerate}




\section*{Certifications}
\begin{itemize}
    \item Open Group Certified Distinguished Architect
    \item IBM Certified Solution Architect - Cloud Platform V4
    \item IBM Certified Developer - Watson v4
    \item IBM Certified Solution Architect - Cloud Pak for Automation v20.0.1
    \item IBM Certification Exam Developer 2020 - Level I
    \item OMG-Certified UML Professional Fundamental
    \item Oracle Certified Programmer, Java SE 7 Programmer
    \item Oracle Certified Associate, Java SE 7 Programmer
\end{itemize}    

\subsection{References}
Available upon request.
\end{document}
